---
title: "Demo of the OBIShmpr package"
author: "Anna Krystalli"
date: "18/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install

``` r
# install.packages("remotes")
remotes::install_github("annakrystalli/OBIShmpr")
```

```{r}
library(OBIShmpr)
```


## Aim: Match commercial shellfish species to environmental data


### Species

```{r}
species_names <- c("Crassostrea gigas", "Palinurus elephas")
```

```{r}
species_ids <- worrms::wm_name2id_(species_names) %>%
    unlist()
```

```{r}

ostrea_edulis_id <- worrms::wm_records_name("Ostrea edulis") %>% 
    dplyr::filter(status == "accepted") %>%
    dplyr::pull(valid_AphiaID)

species_ids <- c(species_ids, ostrea_edulis_id) %>%
    setNames(c(species_names, "Ostrea edulis"))

species_ids
```


### Environmental layers

#### Available layers

Available layer in `OBIShmpr`

```{r}
DT::datatable(layer_info)
```



```{r}
layer_codes <- c("BO_ph", "BO_phosphate", 
                 "BO2_phosphatemean_bdmax", 
                 "BO_nitrate", "BO2_nitratemean_bdmax", 
                 "surface_nitrogen", "tn", "surface_carbon",
                 "BO_sstmean", "BO_sstmin", "BO_sstmax", 
                 "MS_biogeo13_sst_mean_5m", "MS_biogeo14_sst_min_5m",
                 "MS_biogeo15_sst_max_5m")
```

## Match species to environmental data

To query, I provide a valid Aphia ID to argument `sp_id`. I'm also limiting the search by providing one of the in-build bounding box geometries, in this case the North Western European Shelf (`bbox_nwes`)).


### _Crassostrea gigas_

I start with the AphiaID for _Crassostrea gigas_.

```{r}
sp_id1 <- species_ids[1]
data_spp1 <- OBIShmpr::obis_match_habitat(sp_id = sp_id1, 
                                          layers = layer_codes,
                                          geometry = bbox_nwes)

data_spp1
```

### _Palinurus elephas_

Next I use the AphiaID for _Palinurus elephas_.

```{r}
sp_id2 <- species_ids[2]

data_spp2 <- OBIShmpr::obis_match_habitat(
    sp_id = sp_id2, 
    layers = layer_codes,
    geometry = bbox_nwes)

data_spp2
```


## Plot

```{r}
library(ggplot2)
world <- rnaturalearth::ne_countries(scale = "medium", returnclass = "sf")


ggplot() +
    geom_sf(data = world) +
    geom_sf(data = data_spp1, aes(color = BO_ph) ) +
    coord_sf(crs = 3035,
             xlim = c(2426378.0132, 7093974.6215),
             ylim = c(1308101.2618, 5446513.5222)) +
    theme_bw() +
    ggtitle(names(sp_id1),
            subtitle = paste0('AphiaID = ', sp_id1))

```


```{r}
library(ggplot2)
world <- rnaturalearth::ne_countries(scale = "medium", returnclass = "sf")


ggplot() +
    geom_sf(data = world) +
    geom_sf(data = data_spp2, aes(color = BO_ph) ) +
    coord_sf(crs = 3035,
             xlim = c(2426378.0132, 7093974.6215),
             ylim = c(1308101.2618, 5446513.5222)) +
    theme_bw() +
    ggtitle(names(sp_id2),
            subtitle = paste0('AphiaID = ', sp_id2))

```

